---
title: "Amazon Stock Analysis Report"
author: "Kutay İLİ"
date: "`r Sys.Date()`"
output: html_document
---



```{r setup, include = FALSE}
# Load necessary libraries
library(knitr)
library(rmarkdown)
library(quantmod)
library(tseries)
library(timeSeries)
library(forecast)
library(xts)
library(leaflet)
library(dplyr)
library(htmltools)
library(rvest)
library(urca)
```
## Introduction

In this analysis, we will explore the stock prices of Amazon (AMZN) using various time series analysis techniques and visualizations.

### Amazon Stock Analysis

```{r Amazon Stock Analysis, echo=FALSE, warning=FALSE}
getSymbols('AMZN', from= '2019-01-01', to = Sys.Date())
AMZN_Close_Prices = AMZN[,4]

plot(AMZN_Close_Prices)

par(mfrow=c(1,2))
Acf(AMZN_Close_Prices, main = 'ACF for Differenced Series')
Pacf(AMZN_Close_Prices, main = 'PACF for Differenced Series')

print(adf.test(AMZN_Close_Prices)) #p-value = 0.7027
auto.arima(AMZN_Close_Prices, seasonal = FALSE) # ARIMA(0,1,0) AIC/BIC = 6183/6188

fitA = auto.arima(AMZN_Close_Prices, seasonal = FALSE)
tsdisplay(residuals(fitA), lag.max = 40, main = '(0,1,0) Model Residuals')
auto.arima(AMZN_Close_Prices, seasonal = FALSE) # AIC/BIC = 6183/6188

fitB = arima(AMZN_Close_Prices, order = c(2,1,1))
tsdisplay(residuals(fitB), lag.max = 40, main = '(2,1,1) Model Residuals')

fitC = arima(AMZN_Close_Prices, order = c(2,2,2))
tsdisplay(residuals(fitC), lag.max = 40, main = '(2,2,2 Model Residuals')

fitD = arima(AMZN_Close_Prices, order = c(1,1,1))
tsdisplay(residuals(fitD), lag.max = 40, main = '(1,1,1) Model Residuals')

cat("PLOTS")
par(mfrow=c(2,2))

term <- 90
fcast1 <- forecast(fitA, h = term)
plot(fcast1)

fcast2 <- forecast(fitB, h = term)
plot(fcast2)
fcast3 <- forecast(fitC, h = term)
plot(fcast3)
fcast4 <- forecast(fitD, h = term)
plot(fcast4)

cat("Mape accuracy")
cat(" ARIMA 1")
accuracy(fcast1) # mape = 1.581473, accuracy = 98.41853%
cat(" ARIMA 2")
accuracy(fcast2) # mape = 1.582399, accuracy = 98.4176%
cat(" ARIMA 3")
accuracy(fcast3) # mape = 1.578755, accuracy = 98.42125% highest
cat(" ARIMA 4")
accuracy(fcast4) # mape = 1.584466, accuracy = 98.415534%
```

### Amazon Volume Analysis

```{r Amazon Volume Analysis, echo= FALSE, message=FALSE, warning=FALSE}

getSymbols('AMZN', from= '2019-01-01', to = Sys.Date())
AMZN_Volume = AMZN[,5]

plot(AMZN_Volume)

par(mfrow=c(1,2))
Acf(AMZN_Volume, main = 'ACF for Differenced Series')
Pacf(AMZN_Volume, main = 'PACF for Differenced Series')

print(adf.test(AMZN_Volume)) #p-value = 0.01(p-value smaller than printed p-value)
auto.arima(AMZN_Volume, seasonal = FALSE) # ARIMA(1,1,1) AIC/BIC = 46712.8/46728.23

fitE = auto.arima(AMZN_Volume, seasonal = FALSE)
tsdisplay(residuals(fitE), lag.max = 40, main = '(1,1,1) Model Residuals')
auto.arima(AMZN_Volume, seasonal = FALSE) # AIC/BIC = 46712.8/46728.23

fitF = arima(AMZN_Volume, order = c(2,1,1))
tsdisplay(residuals(fitF), lag.max = 40, main = '(2,1,1) Model Residuals')

fitG = arima(AMZN_Volume, order = c(2,2,2))
tsdisplay(residuals(fitG), lag.max = 40, main = '(2,2,2 Model Residuals')

fitH = arima(AMZN_Volume, order = c(3,1,1))
tsdisplay(residuals(fitH), lag.max = 40, main = '(3,1,1) Model Residuals')

cat("PLOTS")
par(mfrow=c(2,2))

#auto arima
term <- 90
fcast5 <- forecast(fitE, h = term)
plot(fcast5)

#custom arimas
fcast6 <- forecast(fitF, h = term)
plot(fcast6)
fcast7 <- forecast(fitG, h = term)
plot(fcast7)
fcast8 <- forecast(fitH, h = term)
plot(fcast8)

cat("Mape accuracy")
cat(" ARIMA 1")
accuracy(fcast5) # mape = 22.14879 , accuracy = 77.85121%
cat(" ARIMA 2")
accuracy(fcast6) # mape = 22.16384  , accuracy = 77.83616%
cat(" ARIMA 3")
accuracy(fcast7) # mape = 21.41623  , accuracy = 78.58377% highest
cat(" ARIMA 4")
accuracy(fcast8) # mape = 22.18992   , accuracy = 77.81008%
```


### Amazon Total Assets Analysis


```{r Amazon Total Assets Analysis, echo=FALSE, warning=FALSE}

#Grabbing table and transforming into the necessary conditions
url <- "https://stockanalysis.com/stocks/amzn/financials/balance-sheet/?p=quarterly"

page <- read_html(url)

table_data <- page %>% html_table(fill = TRUE)

target_table <- NULL
for (table in table_data) {
  if ("Total Assets" %in% colnames(table)) {
    target_table <- table
    break
  }
}
```
```{r, include = FALSE}
if (!is.null(target_table)) {
  total_assets_data <- target_table[, c("Item", "Total Assets")]
  print(total_assets_data)
} else {
  print("Table not found.")
}
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
total_assets <- table[12,1:21]
total_asset <- data.frame(table = as.numeric(gsub(",", "", t(total_assets[ , -1]))))

total_asset_list <- as.list(total_asset$table)

total_asset_list <- rev(total_asset_list)

total_asset_df <- data.frame(Values = unlist(total_asset_list))

total_asset_ts <- ts(total_asset_df$Values, 
                     start = c(2018, 4),
                     frequency = 4) 
print(total_asset_ts)




#Forecasting
plot(total_asset_ts)

par(mfrow=c(1,2))
Acf(total_asset_ts, main = 'ACF for Differenced Series')
Pacf(total_asset_ts, main = 'PACF for Differenced Series')

print(adf.test(total_asset_ts)) #p-value = 0.7505
auto.arima(total_asset_ts, seasonal = FALSE) # ARIMA(0,1,0)  AIC/BIC = 422.68/424.57

fitX = auto.arima(total_asset_ts, seasonal = FALSE)
tsdisplay(residuals(fitX), lag.max = 40, main = '(1,1,1) Model Residuals')
auto.arima(total_asset_ts, seasonal = FALSE) # AIC/BIC = 46712.8/46728.23

fitY = arima(total_asset_ts, order = c(2,1,1))
tsdisplay(residuals(fitF), lag.max = 40, main = '(2,1,1) Model Residuals')

fitZ = arima(total_asset_ts, order = c(2,2,1))
tsdisplay(residuals(fitG), lag.max = 40, main = '(2,2,2 Model Residuals')

fitI = arima(total_asset_ts, order = c(1,1,1))
tsdisplay(residuals(fitH), lag.max = 40, main = '(1,1,1) Model Residuals')

cat("PLOTS")
par(mfrow=c(2,2))

#auto arima
term <- 3
fcast9 <- forecast(fitX, h = term)
plot(fcast9)

#custom arimas
fcast10 <- forecast(fitY, h = term)
plot(fcast10)
fcast11 <- forecast(fitZ, h = term)
plot(fcast11)
fcast12 <- forecast(fitI, h = term)
plot(fcast12)

cat("Mape accuracy")
cat(" ARIMA 1")
accuracy(fcast9) # mape = 3.735785, accuracy = 96.264215%
cat(" ARIMA 2")
accuracy(fcast10) # mape = 3.916153, accuracy = 96.083847%
cat(" ARIMA 3")
accuracy(fcast11) # mape = 3.358281, accuracy = 96.641719% highest
cat(" ARIMA 4")
accuracy(fcast12) # mape = 3.944273, accuracy = 96.055727%
```

### Comparison Analysis

#### Amazon and Alibaba

```{r Amazon and Alibaba, echo=FALSE, warning=FALSE}

getSymbols('BABA', from= '2019-01-01', to = Sys.Date())
BABA_Close_Prices = BABA[,4]

plot(BABA_Close_Prices)

par(mfrow=c(1,2))
Acf(BABA_Close_Prices, main = 'ACF for Differenced Series')
Pacf(BABA_Close_Prices, main = 'PACF for Differenced Series')

print(adf.test(BABA_Close_Prices)) #p-value = 0.5394
auto.arima(BABA_Close_Prices, seasonal = FALSE) # ARIMA(0,1,0) AIC/BIC = 7386.77/7433.07

fitBABA = auto.arima(BABA_Close_Prices, seasonal = FALSE)
tsdisplay(residuals(fitBABA), lag.max = 40, main = '(0,1,0) Model Residuals')
auto.arima(BABA_Close_Prices, seasonal = FALSE) # AIC/BIC = 7386.77/7433.07


cat("Auto arima")
term <- 90
fcastBABA <- forecast(fitBABA, h = term)
plot(fcastBABA)

cat("Mape accuracy")
accuracy(fcastBABA) 

# Explore
summary(AMZN_Close_Prices)
summary(BABA_Close_Prices)

# Both Stock Prices
plot(Cl(AMZN_Close_Prices), type = "l", col = "blue", main = "Amazon Stock Prices")
lines(Cl(BABA_Close_Prices), col = "red")
legend("topright", legend = c("Amazon", "Alibaba"), col = c("blue", "red"))

# Relative Performance
relative_performance <- Cl(AMZN_Close_Prices) / Cl(BABA_Close_Prices)
plot(relative_performance, type = "l", col = "black", main = "Relative Performance (Amazon vs. Alibaba)")

merged_data <- merge(Cl(AMZN_Close_Prices), Cl(BABA_Close_Prices), join = "inner")

cat("Calculate Correlation")
correlation <- cor(merged_data[, 1], merged_data[, 2])
print(correlation)

cor_tests1 <- suppressWarnings(cor.test(merged_data[, 1], merged_data[, 2]))
print(cor_tests1)


aligned_data2 <- merge(Cl(AMZN_Close_Prices), Cl(BABA_Close_Prices), join = "inner")

cat("Cointegration test")
cointegration_test <- ca.jo(aligned_data2, type = "eigen", K = 2, ecdet = "const", spec = "longrun")
print(cointegration_test)

summary(cointegration_test)

relative_performance_alibaba <- Cl(AMZN_Close_Prices) / Cl(BABA_Close_Prices)

dates_alibaba <- index(AMZN_Close_Prices)
relative_performance_ts_alibaba <- ts(relative_performance_alibaba, start = dates_alibaba[1], frequency = 1)

# Simple moving average
ma_window_alibaba <- 20
ma_relative_performance_alibaba <- stats::filter(relative_performance_ts_alibaba, rep(1/ma_window_alibaba, ma_window_alibaba), sides = 2)

# Plotting advanced relative performance for Alibaba
plot(relative_performance_ts_alibaba, type = "l", col = "black", lwd = 2,
     main = "Advanced Relative Performance (Amazon vs. Alibaba)",
     ylab = "Relative Performance", xlab = "Time")

# Moving average line
lines(index(relative_performance_ts_alibaba), ma_relative_performance_alibaba, col = "blue", lwd = 2)

# Significant periods
threshold_alibaba <- mean(relative_performance_alibaba)
abline(h = threshold_alibaba, col = "red", lty = 2)


legend("bottomright", legend = c("Relative Performance", "Moving Average", paste("Threshold =", threshold_alibaba)),
       col = c("black", "blue", "red"), lty = c(1, 1, 2), lwd = c(2, 2, 1))
```

#### Amazon and eBay
```{r Amazon and eBay, echo=FALSE, warning=FALSE}

getSymbols('EBAY', from= '2019-01-01', to = Sys.Date())
EBAY_Close_Prices = EBAY[,4]

plot(EBAY_Close_Prices)

# ACF and PACF for differenced series
par(mfrow=c(1,2))
Acf(EBAY_Close_Prices, main = 'ACF for Differenced Series')
Pacf(EBAY_Close_Prices, main = 'PACF for Differenced Series')

# Augmented Dickey-Fuller test
print(adf.test(EBAY_Close_Prices)) # p-value = 0.5394

cat("Auto ARIMA")
auto.arima(EBAY_Close_Prices, seasonal = FALSE) # ARIMA(0,1,0) AIC/BIC = 7386.77/7433.07

# Fit ARIMA model
fitEBAY = auto.arima(EBAY_Close_Prices, seasonal = FALSE)

# Time series display for residuals
tsdisplay(residuals(fitEBAY), lag.max = 40, main = '(0,1,0) Model Residuals')


# Auto ARIMA forecast
term <- 90
fcastEBAY <- forecast(fitEBAY, h = term)
plot(fcastEBAY)

# MAPE accuracy 
accuracy(fcastEBAY) # MAPE = 2.062036, accuracy = 97.937964%

cat("Explore")
summary(AMZN_Close_Prices)
summary(EBAY_Close_Prices)

# Plotting stock prices for Amazon and eBay
plot(Cl(AMZN_Close_Prices), type = "l", col = "blue", main = "Amazon vs. eBay Stock Prices")
lines(Cl(EBAY_Close_Prices), col = "green")
legend("topright", legend = c("Amazon", "eBay"), col = c("blue", "green"))

# Relative performance
relative_performance_ebay <- Cl(AMZN_Close_Prices) / Cl(EBAY_Close_Prices)
plot(relative_performance_ebay, type = "l", col = "black", main = "Relative Performance (Amazon vs. eBay)")

merged_data_ebay <- merge(Cl(AMZN_Close_Prices), Cl(EBAY_Close_Prices), join = "inner")

cat("Correlation")
correlation_ebay <- cor(merged_data_ebay[, 1], merged_data_ebay[, 2])
print(correlation_ebay)

cat(" Cointegration test ")
aligned_data_ebay <- merge(Cl(AMZN_Close_Prices), Cl(EBAY_Close_Prices), join = "inner")
cointegration_test_ebay <- ca.jo(aligned_data_ebay, type = "eigen", K = 2, ecdet = "const", spec = "longrun")
print(cointegration_test_ebay)
summary(cointegration_test_ebay)


# Relative performance for eBay
relative_performance_ebay <- Cl(AMZN_Close_Prices) / Cl(EBAY_Close_Prices)

dates2 <- index(AMZN_Close_Prices)
relative_performance_ts <- ts(relative_performance_ebay, start = dates2[1], frequency = 1)

# Moving average
ma_window <- 20
ma_relative_performance <- stats::filter(relative_performance_ts, rep(1/ma_window, ma_window), sides = 2)

# Advanced relative performance
plot(relative_performance_ts, type = "l", col = "black", lwd = 2,
     main = "Advanced Relative Performance (Amazon vs. eBay)",
     ylab = "Relative Performance", xlab = "Time")

lines(index(relative_performance_ts), ma_relative_performance, col = "blue", lwd = 2)

# Significant periods

threshold_EBAY <- mean(relative_performance_ebay)
abline(h = threshold_EBAY, col = "red", lty = 2)

# Add legend
legend("bottomright", legend = c("Relative Performance", "Moving Average", paste("Threshold =", threshold_EBAY)),
       col = c("black", "blue", "red"), lty = c(1, 1, 1), lwd = c(1, 1, 1))
```

#### Amazon and Walmart
```{r Amazon and Walmart, echo=FALSE, warning=FALSE}

getSymbols('WMT', from= '2019-01-01', to = Sys.Date())
WMT_Close_Prices = WMT[,4]

# Plot Walmart stock prices
plot(WMT_Close_Prices)

# ACF and PACF for differenced series
par(mfrow=c(1,2))
Acf(WMT_Close_Prices, main = 'ACF for Differenced Series')
Pacf(WMT_Close_Prices, main = 'PACF for Differenced Series')

# Augmented Dickey-Fuller test
print(adf.test(WMT_Close_Prices)) # p-value = 0.5394

cat("Auto ARIMA")
auto.arima(WMT_Close_Prices, seasonal = FALSE) # ARIMA(0,1,0) AIC/BIC = 7386.77/7433.07


fitWMT = auto.arima(WMT_Close_Prices, seasonal = FALSE)


tsdisplay(residuals(fitWMT), lag.max = 40, main = '(0,1,0) Model Residuals')


term <- 90
fcastWMT <- forecast(fitWMT, h = term)
plot(fcastWMT)


accuracy(fcastWMT) # MAPE = 2.062036, accuracy = 97.937964%

cat("Explore")
summary(AMZN_Close_Prices)
summary(WMT_Close_Prices)


plot(Cl(AMZN_Close_Prices), type = "l", col = "blue", main = "Amazon vs. Walmart Stock Prices")
lines(Cl(WMT_Close_Prices), col = "purple")
legend("topright", legend = c("Amazon", "Walmart"), col = c("blue", "purple"))


relative_performance_walmart <- Cl(AMZN_Close_Prices) / Cl(WMT_Close_Prices)
plot(relative_performance_walmart, type = "l", col = "black", main = "Relative Performance (Amazon vs. Walmart)")


merged_data_walmart <- merge(Cl(AMZN_Close_Prices), Cl(WMT_Close_Prices), join = "inner")

cat(" Correlation")
correlation_walmart <- cor(merged_data_walmart[, 1], merged_data_walmart[, 2])
print(correlation_walmart)

cat("Cointegration test")
aligned_data_walmart <- merge(Cl(AMZN_Close_Prices), Cl(WMT_Close_Prices), join = "inner")
cointegration_test_walmart <- ca.jo(aligned_data_walmart, type = "eigen", K = 2, ecdet = "const", spec = "longrun")
print(cointegration_test_walmart)

summary(cointegration_test_walmart)


relative_performance_walmart <- Cl(AMZN_Close_Prices) / Cl(WMT_Close_Prices)

dates_walmart <- index(AMZN_Close_Prices)
relative_performance_ts_walmart <- ts(relative_performance_walmart, start = dates_walmart[1], frequency = 1)

ma_window_walmart <- 20
ma_relative_performance_walmart <- stats::filter(relative_performance_ts_walmart, rep(1/ma_window_walmart, ma_window_walmart), sides = 2)

plot(relative_performance_ts_walmart, type = "l", col = "black", lwd = 2,
     main = "Advanced Relative Performance (Amazon vs. Walmart)",
     ylab = "Relative Performance", xlab = "Time")


lines(index(relative_performance_ts_walmart), ma_relative_performance_walmart, col = "blue", lwd = 2)

threshold_walmart <- mean(relative_performance_walmart)
abline(h = threshold_walmart, col = "red", lty = 2)


legend("bottomright", legend = c("Relative Performance", "Moving Average", paste("Threshold =", threshold_walmart)),
       col = c("black", "blue", "red"), lty = c(1, 1, 2), lwd = c(2, 2, 1))

```

#### News about Amazon

  In this section, the news about Amazon from the last 30 days can be found. The content includes dates, news headlines, and links to access the news. In the final section, the current stock price of Amazon is displayed.
  

#### Interactive Map of Amazon's Global Expansion

  In this section, countries are categorized based on the dates when Amazon commenced operations, and this information is visualized on an interactive map.

```{r, warning=FALSE ,echo=FALSE}
library(leaflet)
library(dplyr)
library(htmltools)
library(rvest)



wiki_url <- "https://en.wikipedia.org/wiki/Amazon_(company)"


wiki_page <- read_html(wiki_url)


amazon_table <- wiki_page %>% html_nodes(".wikitable") %>% html_table(fill = TRUE)


amazon_data <- amazon_table[[1]]


country_column <- amazon_data$Country
since_column <- amazon_data$Since


amazon_df <- data.frame(Country = country_column, Since = since_column)

print(amazon_df)



amazon_df$Lat <- c(26.8206, -14.2350, 56.1304, 23.6345, 37.0902, 35.8617, 20.5937, 
                   36.2048, 23.8859, 1.3521, 38.9637, 23.4241, 50.8503, 46.6031, 
                   51.1657, 41.8719, 52.1326, 51.9194, 40.4637, 60.1282, 55.3781, 
                   -25.2744)

amazon_df$Long <- c(30.8025, -51.9253, -106.3468, -102.5528, -95.7129, 104.1954, 
                    78.9629, 138.2529, 45.0792, 103.8198, 35.2433, 53.8478, 4.3517, 
                    1.8883, 10.4515, 12.5674, 5.2913, 19.1451, -3.7492, 18.6435, 
                    -3.4360, 133.7751)






country_column <- amazon_data$Country
since_column <- amazon_data$Since

amazon_df$Year <- as.numeric(gsub("\\D", "", amazon_df$Since))

amazon_df$Category <- cut(amazon_df$Year, breaks = c(0, 2000, 2010, 2015, 2020, Inf), labels = c("<2000", "2000-2010", "2010-2015", "2015-2020", "2020<"))



category_colors <- colorFactor(c("red", "orange", "yellow", "green", "blue"), levels = c("<2000", "2000-2010", "2010-2015", "2015-2020", "2020<"))



amazon_map <- leaflet(amazon_df) %>%
  addTiles() %>%
  addCircleMarkers(
    lat = ~ Lat,  # Replace with your latitude column
    lng = ~ Long,  # Replace with your longitude column
    radius = 8,
    color = ~category_colors(Category),
    fillOpacity = 0.7,
    popup = ~paste(Country, "<br>Since:", Since, sep = " ")
  ) %>%
  addLegend(
    title = "Amazon Countries",
    colors = c("red", "orange", "yellow", "green", "blue"),
    labels = c("<2000", "2000-2010", "2010-2015", "2015-2020", "2020<"),
    position = "bottomright"
  )


amazon_map


```





